Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-07-23 replication_paper/pnas_draft/paper.Rmd
1

save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
          p_precision_combined, base_height = 18, base_width = 24)

>>>>

ratio=1.5
height=18
save_plot(file=paste0(here::here(), '/replication_paper/figures/p_precision_combined.png'),
          p_precision_combined, base_height = 18, base_width = height*ratio)
